---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gitr

<!-- badges: start -->
<!-- badges: end -->

`gitr` is an R package that provides an R wrapper for Git commands. Currently, `gitr` is under development and should be used at your own risk. 

## Installation

You can install the development version of gitr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("graysonwhite/gitr")
```

## Current features

Currently, `gitr` has four functions:    
    - `add()` takes a character vector of file names and calls `git add` on those files to add them to the Git index.    
    - `commit()` calls `git commit` and will, by default, add all new or changed files to the Git index. This behavior can be changed in the function parameters.      
    - `push()` calls `git push`.     
    - `pull()` calls `git pull`.
    
## Simple example

Suppose your working directory is a Git repository with changed and new files `my_function.R`, `text.txt`, and `docs.md`. If you wanted to commit and push these files in R you could:

```{r, eval = F}
library(gitr)

commit(messsage = "My snazzy commit message")

push()
```

However, you may want to only commit one of these files, or use multiple commits. `gitr` can accommodate this, as well: 

```{r, eval = F}
# First, commit two files
commit("My first commit message",
       add_all = FALSE,
       files = c("text.txt", "docs.md"))

commit("add my function",
       add_all = FALSE,
       files = "my_function.R")

push()
```

`gitr` can also add files manually with `add()`, and then `commit()` and `push()` them, like so:
```{r, eval = F}
file.create("some_new_file.txt")

add("some_new_file.txt")

commit(message = "add some new file",
       add_all = FALSE)

push()
```






